---
title: "Reading Tracker"
format: 
  html: 
    self-contained: true
---

On this page you will find all the papers and books that I have read since I started tracking on July 16, 2023. The purpose of this is to encourage both myself and others to read more. 

Please note that the ratings I provide are strictly my personal opinion and I mean no ill will if I rate something of yours poorly. Additionally, if I rate something well that does not mean that I am endorsing the authors; it simply means that I enjoyed reading their work or found it useful.


```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(reactable)
library(plyr)
library(ggimage)
library(gganimate)
library(scales)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
Data <- read_excel("~/Desktop/Reading/Reading.xlsx", sheet = "Complete")
Data$`Date Completed` <- as.Date(Data$`Date Completed`)
```

# Books - Learning
```{r,echo=FALSE, include=TRUE}
Learning_Data <- Data %>% filter(Type == "Book - Learning") %>% select(-c("Type"))
  
reactable(Learning_Data, defaultPageSize = 5, defaultColDef = colDef(align = "center"), searchable = TRUE, striped = TRUE, highlight = TRUE, bordered = TRUE, theme = reactableTheme(borderColor = "black", stripedColor = "#E6E6FA", highlightColor = "#E0FFFF", cellPadding = "8px 12px"))
```

# Books - Leisure
```{r,echo=FALSE, include=TRUE}
Leisure_Data <- Data %>% filter(Type == "Book - Leisure") %>% select(-c("Type"))
  
reactable(Leisure_Data, defaultPageSize = 5, defaultColDef = colDef(align = "center"), searchable = TRUE, striped = TRUE, highlight = TRUE, bordered = TRUE, theme = reactableTheme(borderColor = "black", stripedColor = "#E6E6FA", highlightColor = "#E0FFFF", cellPadding = "8px 12px"))
```

# Papers
```{r,echo=FALSE, include=TRUE}
Paper_Data <- Data %>% filter(Type == "Paper") %>% select(-c("Type"))
  
reactable(Paper_Data, defaultPageSize = 5, defaultColDef = colDef(align = "center"), searchable = TRUE, striped = TRUE, highlight = TRUE, bordered = TRUE, theme = reactableTheme(borderColor = "black", stripedColor = "#E6E6FA", highlightColor = "#E0FFFF", cellPadding = "8px 12px"))
```

# How Much Reading?
```{r, warning=FALSE, message=FALSE, echo=FALSE}
Data <- Data[order(as.Date(Data$`Date Completed`, format="%Y/%m/%d")),]

New_Data <- Data %>% group_by(`Date Completed`) %>% mutate(Pages_Total = cumsum(Pages)) %>% top_n(1, Pages_Total)

New_Data$Days <- round(as.numeric(difftime(New_Data$`Date Completed`, "2023-06-16", units = "days")))

last <- tail(New_Data$Days, 1)

cap <- round_any(tail(New_Data$Pages_Total,1), 100, f=ceiling)

p <- ggplot(New_Data, aes(x= Days, y = Pages_Total)) + geom_line(size = 1.75, aes(color = 'lightblue')) + geom_point() + xlab("Days since June 16, 2023") + ylab("Total Pages Read") + scale_color_manual(values=c("#E6E6FA")) + xlim(0,last) + ylim(0,cap) + theme_classic() + theme(legend.position = "none")  + scale_x_continuous(breaks = pretty_breaks()) + transition_reveal(Days)

animate(p, end_pause = 30)
```

