---
title: "Reading Tracker"
format: 
  html: 
    self-contained: true
---

On this page you will find all the papers and books that I have read since I started tracking on July 16, 2023. The purpose of this is to encourage both myself and others to read more. 

Please note that the ratings I provide are strictly my personal opinion and I mean no ill will if I rate something of yours poorly. Additionally, if I rate something well that does not mean that I am endorsing the authors; it simply means that I enjoyed reading their work or found it useful.


```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(reactable)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
Data <- read_excel("~/Desktop/Reading/Reading.xlsx", sheet = "Complete")
Data$`Date Completed` <- as.Date(Data$`Date Completed`)
```

# Books - Learning
```{r,echo=FALSE, include=TRUE}
Learning_Data <- Data %>% filter(Type == "Book - Learning") %>% select(-c("Type"))
  
reactable(Learning_Data[1:5,], defaultColDef = colDef(align = "center"), searchable = TRUE, striped = TRUE, highlight = TRUE, bordered = TRUE, theme = reactableTheme(borderColor = "black", stripedColor = "#E6E6FA", highlightColor = "#E0FFFF", cellPadding = "8px 12px"))
```

# Books - Leisure
```{r,echo=FALSE, include=TRUE}
Leisure_Data <- Data %>% filter(Type == "Book - Leisure") %>% select(-c("Type"))
  
reactable(Leisure_Data[1:5,], defaultColDef = colDef(align = "center"), searchable = TRUE, striped = TRUE, highlight = TRUE, bordered = TRUE, theme = reactableTheme(borderColor = "black", stripedColor = "#E6E6FA", highlightColor = "#E0FFFF", cellPadding = "8px 12px"))
```

# Papers
```{r,echo=FALSE, include=TRUE}
Paper_Data <- Data %>% filter(Type == "Paper") %>% select(-c("Type"))
  
reactable(Paper_Data[1:5,], defaultColDef = colDef(align = "center"), searchable = TRUE, striped = TRUE, highlight = TRUE, bordered = TRUE, theme = reactableTheme(borderColor = "black", stripedColor = "#E6E6FA", highlightColor = "#E0FFFF", cellPadding = "8px 12px"))
```
